---
title: "R Visualize countries, currencies and population of the world using r2country"
author: "Obi Obianom"
date: "2023-10-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
quickcode::libraryAll(
  r2country,
  collapsibleTree,
  dplyr,
  quietly = TRUE,
  clear = TRUE
)
```

## The What

In this tutorial, we are going to combine the power of 4 R packages to create a nice visual for countries by their respective continents and their capitals.

## Packages used

 - [x] &nbsp; quickcode - clear environment and load required packages, as well as provide useful functions
 - [x] &nbsp; r2country - various datasets for continents, countries, captials, calling code and so on
 - [x] &nbsp; collapsibleTree - create a nice visual using the provided dataset to visualize countries 
 
## Load packages

```{r}
quickcode::libraryAll(
  r2country,
  collapsibleTree,
  quietly = TRUE,
  clear = TRUE
)

```


## Prepare and previous continents and country data from r2country package

```{r}
# use datasets of continent, country names, and capitals

final.dt <- country_names

for (cl in c(
  "country_continent", # continents
  "country_capital", # capitals
  "country_money", # currencies
  "country_population" # population
)) {
  final.dt <- merge(final.dt, get(cl), by = "ID")
}


# preview the dataset
names(final.dt)
head(final.dt)

```


## Visualize the country dataset

*** 

### Continent ⇉ Country ⇉ Captitals

```{r}
collapsibleTree(
  final.dt,
  hierarchy = c("continent", "name", "capital"),
  root = "Continents",
  width = 1800,
  fontSize = 15,
  height = 1000,
  zoomable = TRUE
)
```
***
### Continent ⇉ Country ⇉ Currency
```{r}
collapsibleTree(
  final.dt,
  hierarchy = c("continent", "name", "currency"),
  root = "Continents",
  width = 1800,
  fontSize = 15,
  height = 1000,
  zoomable = TRUE
)
```
***
### Continent ⇉ Country ⇉ Population
```{r}
collapsibleTree(
  final.dt,
  hierarchy = c("continent", "name", "population2023"),
  root = "Continents",
  width = 1800,
  fontSize = 15,
  height = 1000,
  zoomable = TRUE
)
```

***
### Continent ⇉ Country ⇉ isocode
```{r}
collapsibleTree(
  final.dt,
  hierarchy = c("continent", "name", "isocode"),
  root = "Continents",
  width = 1800,
  fontSize = 15,
  height = 1000,
  zoomable = TRUE
)
```

## R package links

 - [x] &nbsp; quickcode - https://cran.r-project.org/package=quickcode
 - [x] &nbsp; r2country - https://cran.r-project.org/package=r2country
 - [x] &nbsp; collapsibleTree - https://cran.r-project.org/package=collapsibleTree
